Shades of Green

### 2023-09-26 docs/presentations/20230928-sehm_presentation.qmd
fix headers in sehm_pres

format:
  revealjs:
    theme: [../assets/revealme.scss]
    transition: none
    title-slide-attributes:
      data-background-image: '../assets/ground-fog-valley-black-forest-sunset.jpg'
      data-background-size: fit
      data-background-opacity: '0.3'
    embed-resources: true

@@

@@

display(
    Markdown(
        f"## SWINNO -- A Swedish Innovation Output Database with {n_swinno} Innovations"
        + "{.smaller}"
    )
)

@@

@@

@@

display(
    Markdown(
        f"## <span class='r-fit-text text-royal-blue-600'>{n_certain_bioeconomy_visions}</span> unique forest bioeconomy innovations classified"
    )
)

@@

unique forest bioeconomy innovations classified

>>>>

format:
  revealjs:
    theme: [../assets/revealme.scss]
    transition: none
    title-slide-attributes:
      data-background-image: '../assets/ground-fog-valley-black-forest-sunset.jpg'
      data-background-size: fit
      data-background-opacity: '0.45'
    embed-resources: true

@@

****

@@

display(
    Markdown(
        f"### SWINNO -- A Swedish Innovation Output Database with {n_swinno} Innovations"
    )
)

@@

[@sjoo2014DatabaseSwedishInnovations]{.slide-cite}

<style>
  h2 {font-size=3rem;}
</style>

@@

```{python}
# | output: asis

@@

text = f"""<span class="r-fit-text">after<b> {n_certain_bioeconomy_visions}</b> unique forest innovations classified</span>"""

display(Markdown(text))

@@
